---
title: "Preliminary Analysis of Air Quality Data"
author: "[Your Team Name]"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This document provides an initial exploration of the air quality dataset to assess its structure, completeness, and basic statistical properties.

## Load Required Libraries
```{r}
library(readxl)
library(dplyr)
library(ggplot2)
```

## Load Dataset
```{r}
# Read the dataset from Excel file
dataset <- read_excel("AirQuality.xlsx")

# Display first few rows
head(dataset)
```

## Data Structure
```{r}
# Check structure of the dataset
str(dataset)

# Summary statistics
summary(dataset)
```

## Missing Values Analysis
```{r}
# Count missing values per column
colSums(is.na(dataset))
```

## Preliminary Data Visualization
### Distribution of Ozone Levels
```{r}
# Ensure Arithmetic Mean is numeric and handle non-numeric values
dataset$`Arithmetic Mean` <- as.numeric(as.character(dataset$`Arithmetic Mean`))

# Filter out missing or zero values
dataset_filtered <- dataset %>% filter(!is.na(`Arithmetic Mean`), `Arithmetic Mean` > 0)

# Check if filtered dataset has valid values
if(nrow(dataset_filtered) > 0) {
  ggplot(dataset_filtered, aes(x = `Arithmetic Mean`)) +
    geom_histogram(binwidth = 0.01, fill = "blue", alpha = 0.7) +
    labs(title = "Distribution of Ozone Levels", x = "Ozone Concentration (ppm)", y = "Count")
} else {
  print("No valid data available for plotting.")
}
```

### Time Series of Ozone Levels (If Date Available)
```{r}
if("1st Max DateTime" %in% colnames(dataset)) {
  dataset$`1st Max DateTime` <- as.POSIXct(dataset$`1st Max DateTime`, format="%m/%d/%Y %H:%M", tz="UTC")
  
  ggplot(dataset, aes(x = `1st Max DateTime`, y = `Arithmetic Mean`)) +
    geom_line(color = "red") +
    labs(title = "Ozone Levels Over Time", x = "Date", y = "Ozone Concentration (ppm)")
}
```

## Conclusion
The dataset has been successfully loaded and explored. Initial findings suggest that the dataset includes multiple pollutant measurements, and missing values may need to be addressed. Further analysis will focus on trends and relationships between pollutants across regions.